Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Additional comment
IRB #

@@

\newtext{All results and data shown here are done in accordance with IRB \# XXX?}

>>>>

\comment{\textit{I did change the lineup scoring - for some reason, I was averaging before (and I hadn't included the third battery of lineups b/c of scoring issues).}}

@@

All results and data shown here are done in accordance with IRB \# 13-581.
